Spatial Analysis

### 2021-06-28 Scripts/spatial_analisis.Rmd
moved the pen. analysis to its own chunk

write_sf(grid_eez_sf, paste0(my_path("D", "Spatial"),"grid_eez_sf.shp"))

@@

@@

grid_eez_sf <-  st_read("/Volumes/Enterprise/Data/AcrossBoundaries/Data/Spatial/grid_sf/grid_eez_sf.shp")

unique(grid_eez_sf$state)

@@

grid_eez_df <- as.data.frame(grid_eez_sf) %>%
  select(state,index) %>% 
  left_join(ne_grid, 
            by = "index")

write_csv(grid_eez_df, paste0(my_path("R", "Partial"),"grid_eez_df.csv"))

# DONE!

>>>>

# write_sf(grid_eez_sf, paste0(my_path("D", "Spatial"),"grid_eez_sf.shp"))

@@

```{r remove_pen, eval = F, echo = F}

####____________________________________________### 
# Solving for Issue #8 Pennsylvania has NO coast
####____________________________________________###

@@

# grid_eez_sf <-  st_read("/Volumes/Enterprise/Data/AcrossBoundaries/Data/Spatial/grid_sf/grid_eez_sf.shp")

# unique(grid_eez_sf$state)

@@

# grid_eez_df <- as.data.frame(grid_eez_sf) %>%
  # select(state,index) %>%
  # left_join(ne_grid,
            # by = "index")

# write_csv(grid_eez_df, paste0(my_path("R", "Partial"),"grid_eez_df.csv"))
```
